Manuscript figures

### 2024-04-04 04_manuscript_plots.Rmd
minor edits

all_chla <- chla_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(model_meta) |> 
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps),
         ast = ifelse(mean_crps < -100, '*', ''),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no'), 
         uses_AT = as.factor(str_detect(NOAA_var, 'air_temperature')),
         mean_crps = ifelse(mean_crps < -100, -100, mean_crps)) |> 
  ggplot(aes(x=mean_crps, y = manuscript_name, fill = model_type)) +
  annotate('rect', xmax = Inf, xmin = -Inf, ymin = 19.5, ymax =  Inf, fill = 'grey', alpha = 0.2) + 
  geom_bar_pattern(aes(pattern = uses_AT),# Different pattern for each group
                   stat = "identity",
                   alpha = 0.8, 
                   colour = 'black',
                   pattern_fill = "black",
                   pattern_colour = "black", width = 0.8,
                   pattern_spacing = 0.03,
                   pattern_alpha = 1) + 
  scale_y_reordered() +
  labs(y='Model', x = 'Mean relative skill (ug/L)', subtitle = 'Chlorophyll a') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe'), name = 'Uses air temperature as a covariate?') +
  scale_pattern_type_manual(values=c(NA, NA), name = 'Uses air temperature as a covariate?') +
  theme_bw()+
  theme(legend.position = 'none')  +
  coord_cartesian(xlim = c(-10, 5)) +
  geom_text(aes(y=manuscript_name, x= 0.5, label = ast), inherit.aes = F)

@@

A <- temperature_skill |> 
  left_join(model_meta, by = 'model_id') |>
  filter(model_type != 'null') |> 
  group_by(model_type, model_id, site_id) |> 
  summarise(mean_skill = mean(skill_crps, na.rm = T)) |>  
  ggplot(aes(x = mean_skill, 
             y = site_id, 
             colour = model_type)) +
  geom_vline(xintercept = 0, linetype = 'solid') +
  geom_text(data = n_model_type, aes(label = paste0('n = ', n)))+ 
  geom_boxplot() +
  facet_wrap(~model_type, scales = 'free_y',nrow = 2) +
  labs(y='Site', x = 'Mean relative skill (°C)') +
  scale_colour_manual(values = cols_modeltype, name = 'Model class') +
  theme_bw()

@@

cowplot::plot_grid(A, B, nrow = 2, rel_heights = c(1.5, 1), align = 'v', axis = 'lr', labels = 'auto') |> 
  ggsave(filename = './Plots/Figure5.png', width = 19, height = 16, units = 'cm')
```

>>>>

all_chla <- chla_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(model_meta) |> 
  mutate(manuscript_name = fct_reorder(manuscript_name, mean_crps),
         ast = ifelse(mean_crps < -100, '>>>', ''),
         uses_NOAA = ifelse(uses_NOAA == 1, 'yes', 'no'), 
         uses_AT = as.factor(str_detect(NOAA_var, 'air_temperature')),
         mean_crps = ifelse(mean_crps < -100, -100, mean_crps)) |> 
  ggplot(aes(x=mean_crps, y = manuscript_name, fill = model_type)) +
  annotate('rect', xmax = Inf, xmin = -Inf, ymin = 19.5, ymax =  Inf, fill = 'grey', alpha = 0.2) + 
  geom_bar_pattern(aes(pattern = uses_AT),# Different pattern for each group
                   stat = "identity",
                   alpha = 0.8, 
                   colour = 'black',
                   pattern_fill = "black",
                   pattern_colour = "black", width = 0.8,
                   pattern_spacing = 0.03,
                   pattern_alpha = 1) + 
  scale_y_reordered() +
  labs(y='Model', x = 'Mean relative skill (ug/L)', subtitle = 'Chlorophyll a') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe'), name = 'Uses air temperature as a covariate?') +
  scale_pattern_type_manual(values=c(NA, NA), name = 'Uses air temperature as a covariate?') +
  theme_bw()+
  theme(legend.position = 'none')  +
  coord_cartesian(xlim = c(-10, 5)) +
  geom_text(aes(y=manuscript_name, x= 0.5, label = ast), inherit.aes = F)

@@

A <- temperature_skill |> 
  left_join(model_meta, by = 'model_id') |>
  filter(model_type != 'null') |> 
  group_by(model_type, model_id, site_id) |> 
  summarise(mean_skill = mean(skill_crps, na.rm = T)) |>  
  ggplot(aes(x = mean_skill, 
             y = site_id, 
             colour = model_type)) +
  geom_vline(xintercept = 0, linetype = 'solid') +
  geom_text(data = n_model_type, aes(label = paste0('n = ', n)))+ 
  geom_boxplot() +
  facet_wrap(~model_type, scales = 'free_y',nrow = 2) +
  labs(y='Site', x = 'Mean relative skill (°C)') +
  scale_colour_manual(values = cols_modeltype, name = 'Model class') +
  theme_bw()  +
  theme(legend.position = 'bottom')

@@

cowplot::plot_grid(A, B, nrow = 2, rel_heights = c(1.5, 1), align = 'v', axis = 'tlbr', labels = 'auto') |> 
  ggsave(filename = './Plots/Figure5.png', width = 19, height = 16, units = 'cm')
```
